---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# latch

<!-- badges: start -->
[![R-CMD-check](https://github.com/latchbio/latch-sdk-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/latchbio/latch-sdk-r/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->



## Installation

### Latest release from CRAN

```r
pak::pak("latch")
```

or

```r
install.packages("latch")
```

### Development version from GitHub

```r
pak::pak("latchbio/latch-sdk-r")
```

or

``` r
# install.packages("devtools")
devtools::install_github("latchbio/latch-sdk-r")
```

## Example

```{r example, eval = FALSE}
library(latch)

acc <- latch::Account$current()
cat("Current account is ")
acc$print()

projects <- acc$list_registry_projects()
cat("Latch Registry for", acc$get_display_name(), "\n")
for (proj in projects) {
  cat(proj$get_display_name(), "\n")
  tables <- proj$list_tables()
  for (table in tables) {
    cat("  -", table$get_display_name(), "\n")
  }
}
```

## Copying/License

This software and text is quad-licensed and downstream users are free to use any of the provided licenses.

**Available licenses:**

| Name           | Requirements | [OSI][1] Approved      | Notes                                                                  |
| -------------- | ------------ | ---------------------- | ---------------------------------------------------------------------- |
| [MIT][2]       | Attribution  | :white_check_mark: Yes | Most commonly recognized and understood                                |
| [BSD0][3]      | None         | :white_check_mark: Yes | Unencumbered license allowed at Google                                 |
| [CC0][4]       | None         | :x: No                 | Preferred way of dedicating software to the public domain              |
| [Unlicense][5] | None         | :white_check_mark: Yes | OSI approved public domain dedication. **Questionable legal standing** |

[1]: https://opensource.org/
[2]: ./mit.license
[3]: ./bsd0.license
[4]: ./copying
[5]: ./unlicense

